The Driving Forces Behind API Evolution

### 2015-05-19 thesis/paper.tex
Started disc

The changes related to functionality being added, modified (deprecated) or removed were predicted with a 100\% accuracy. These changes were deemed the most significant by the interviewee, and it was expressed during the interivew that the these types of changes were the main driving factor behind the development of the new version. On the contrary, three out of five changes which were unrelated to functionality were correctly predicted. The two changes which were not predicted correctly were inaccurate because the main type was confused with the secondary type. This shows that, although the prediction was incorrect, the general reasoning was correct. The changes which had no secondary type were all predicted correctly, which further shows that changes with several types can be diffuse.

\section{Discussion} \label{discussion}
Our results have provided valuable insight into the motives behind the evolution of APIs. The results show that APIs definitely can be studied from the point of view of long-established software evolution theories. Based on the results, we have formulated the subsequent outcomes.

@@

1. 
       %Answer to RQ
       Functionality is the main driver for change, and it catalyses other changes

       %Point to results
       relate to enhanicve types
       relate to functuonality related laws

>>>>

The changes related to functionality being added, modified (deprecated) or removed were predicted with a 100\% accuracy. These changes were deemed the most significant by the interviewee, and it was expressed during the interview that the these types of changes were the main driving factor behind the development of the new version. On the contrary, three out of five changes which were unrelated to functionality were correctly predicted. The two changes which were not predicted correctly were inaccurate because the main type was confused with the secondary type. This shows that, although the prediction was incorrect, the general reasoning was correct. The changes which had no secondary type were all predicted correctly, which further shows that changes with several types can be diffuse.

\section{Discussion} \label{discussion}
In this section, we will, based on the results of our study, answer the research questions and discuss the implications of our work, both for academia and practice.

@@

Our results show that the major driving force for change in APIs is the push (!!!reword) for functionality. The classification of the types of software evolution and software maintenance showed that enhancive changes which either aimed to add brand-new (!!!reword) modules or adding functionality to existing modules were the most common. We also think that it is interesting to note that a majority of the changes which did not affect functionality, such as the updative changes, were spurred because of previous changes which were related to functionality. Following this line of thought, the hunger (!!!reword?) for functionality can be seen as a catalyst for other driving forces to occur (!!!reword). The view of considering functionality to be a major driver for change is supported by the analysis with Lehman's laws. In the law of Continuing Change, Lehman concludes that ``an E-type system must be continually adapted or it becomes progressively less satisfactory". The results of our work supports this view, as the changes did not only add functionality, but it was also found that the application developers most major concern were updates to functionality.

1.

       %Answer to RQ
       Functionality is the main driver for change, and it catalyses other changes

       %Point to results
       relate to enhancive types
       relate to functionality related laws
